Reproducible Validation and Replication Studies in Nanoscale Physics

### 2020-08-12 tex/ClementiBarba2020.tex
edit acknowledgements

>>>>

\section*{Acknowledgments}

We thank Dr. Chase T. Ellis  and Dr. Joseph G. Tischler for the fruitful discussions regarding their results \cite{ellis2016}, 
which led to the validation of \pygbe, and for providing a mesh file and dielectric data that made the modeling closer to their original setup.
We also thank Dr. Christopher D. Cooper for many valuable discussions that helped us overcome some of the challenges faced throughout this work.

This research is supported by the National Science Foundation under Award \#1747669 of the Computer and Information Science and Engineering (CISE) Directorate.
